17th International Satisfiability Modulo Theories Competition (SMT-COMP 2022): Rules and Procedures

### 2022-05-16 rules/rules22.tex
Proof track description

\header{Input/Output.}
The SMT-LIB language provides a command \akey{(get-proof)}, which asks
a solver to output the proof after a \akey{check-sat}
command returns \texttt{unsat}.
This proof must be an s-expression according to the SMT-LIB standard, but
the format is not specified further.
%
Solvers must respond to each command in the benchmark script with the
answers defined in the SMT-LIB format specification.  In particular,
solvers that respond \texttt{unknown} to the \akey{check-sat} command
must respond with an error to the following \akey{get-proof}
command.

The output of the solver is then fed to a proof checker, which also needs to be
provided by the solver authors (but it does not need to authored by them).
%
The input to the proof checker is the whole output of the solver including the
\texttt{unsat} reply to the \akey{check-sat} command.
%
The proof checker's output should start with a line containing either
\texttt{valid} or \texttt{invalid} to indicate that the proof was valid.
%
The rest of the output can be arbitrary (for example the proof checker may print
out statistics).

\header{Result.}
The result of a solver is considered \emph{erroneous} if (i) the
response to the \akey{check-sat} command is \texttt{sat}, (ii) the
proof checker returns \akey{invalid} to the given proof.  Because the
\prooftrack is non-competitive and because there is no common
definition of a valid proof, there will be no score computed for this
track.

@@

\header{Post-Processor.}
This track will use
{\url{https://github.com/SMT-COMP/postprocessors/tree/master/proof-track/process}}
as a post-processor
to validate and accumulate the results.

>>>>

\header{Input/Output Solver.}
For the \prooftrack, solver authors should provide two new scripts
with their solver.  The first script
\texttt{starexec\_solver\_default} takes the name of the benchmark file as
single argument and should run the solver on the benchmark.
As describe in Section~\ref{sec:logistics}, the benchmark
contains the commands \akey{(check-sat)} and \akey{(get-proof)}.
The solver must output the answers to both of these commands to stdout.
Output to stderr is ignored by the toolchain.

Solvers must respond to each command in the benchmark script with the
answers defined in the SMT-LIB format specification.  If the solver
outputs a proof, this proof must be an s-expression according to the
SMT-LIB standard, but the format is not specified further.  Solvers
that respond \texttt{unknown} to the \akey{check-sat} command should
respond with an error to the following \akey{get-proof} command.  Note
that the SMT-LIB conformant error result should be output to stdout.

\header{Input/Output Checker.}
The second script \texttt{starexec\_checker\_default} takes as input
the benchmark file name as first argument and the proof output of the
solver script as second argument.  Note that this proof output will
usually start with the \akey{unsat} result of the \akey{(check-sat)}
command, which the checker must either parse or skip.

The checker should check the provided proof and provide the result to
stdout.  Result printed to stderr is ignored.  The first line of the
proof checker should be one of \akey{valid}, \akey{invalid},
\akey{holey}, \akey{sat}, \akey{unknown}.  The answer \akey{valid}
must only be given, if the checker made sure using the proof that the
benchmark is unsat.  A checker that returns \akey{valid} to a
satisfiable benchmark is deemed to be unsound.  The answer
\akey{invalid} should be returned if the proof is errorneous or
otherwise malformed.  If the proof is correct but skips some proof
steps or if side-conditions for a rule are not checked by the proof
checker, the answer should be \akey{holey}.  The answer \akey{sat}
should be given if the solver claimed that the benchmark is
satisfiable and \akey{unknown} should be given, if the solver answered
\akey{unknown} or if it did not give a proof or gave an error result.

After this firsts line, the proof checker can give arbitrary key/value
pairs of the form \akey{key=value} after the results.  These will be
collected in the final result table and can include information about
the number of proof steps, the number of nodes in the proof, the number
of holes, the number of different proof rules, etc.

\header{Result.}
The result of a solver is considered \emph{erroneous} if (i) the
response to the \akey{check-sat} command is \texttt{sat} and the
benchmark is unsat, (ii) the proof checker returns \akey{invalid} to
the given proof.  Because the \prooftrack is non-competitive and
because there is no common definition of a valid proof, there will be
no score computed for this track.

A proof checker is considered unsound if it returns \akey{valid} for
an invalid proof or for a proof containing unchecked steps.  In
particular, if a proof checker can be tricked to return \akey{valid}
for a satisfiable benchmark, it is unsound.  Thus, a proof checker
must also check that the formula that was proved corresponds to the
benchmark given.  Soundness of the proof checker is a central
criterion by which the participants will be judged.

@@

\header{Wrapper and Post-Processor.}

Solvers in this track will be wrapped in the competition to include the script
{\url{https://github.com/SMT-COMP/postprocessors/tree/master/proof-track/starexec_run_default}}, which calls the solver and checker script.
The track will use
{\url{https://github.com/SMT-COMP/postprocessors/tree/master/proof-track/process}}
as a post-processor
to validate and accumulate the results.
